Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-13 prob.tex
prob.tex \section{Proofs} Fix a defintion...

\begin{definition}\cite{Hatcher2001}~The unit sphere in $\mathbb{R}^{d}$
is denoted by $S^{d-1}=\left\{ \ket{\psi}\in\mathbb{R}^{d}\middle|\ip{\psi}{\psi}=1\right\} $.\qed\end{definition}

>>>>

\begin{definition}\cite{Hatcher2001,dryden2005}~The unit sphere
in $\mathbb{R}^{d}$ is denoted by $S^{d-1}=\left\{ \ket{\psi}\in\mathbb{R}^{d}\middle|\ip{\psi}{\psi}=1\right\} $,
while the unit sphere in $\mathbb{C}^{d}$ is denoted by $\mathbb{C}S^{d-1}=\left\{ \ket{\psi}\in\mathbb{C}^{d}\middle|\ip{\psi}{\psi}=1\right\} $.
Since $\mathbb{C}$ is one-to-one correspondence to $\mathbb{R}^{2}$~\cite{GAMELIN2003},
$\mathbb{C}S^{d-1}$ has the same structure as $S^{2d-1}$. Here,
we use different symbol because they are embedded in different spaces.\qed\end{definition}
